\documentclass[draftthesis]{neiuthesis} 

\usepackage{amsmath}
\usepackage{natbib}
\usepackage[prependcaption]{todonotes} %[obeyDraft]
\usepackage{Sweave}
% changes to Sweave.sty defaults
% from http://faculty.agecon.vt.edu/moeltner/AAEC5126/Sweave/docs/Arnholt_tutorial.pdf
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontsize=\small,fontshape=n}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{fontsize=\small,fontshape=n}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontsize=\small,fontshape=n}
\usepackage{graphicx}
\usepackage{listings} 
\usepackage{courier} 
\lstset{breaklines=true,basicstyle=\ttfamily,language=R}
\usepackage{pdfpages}
\usepackage{pbox}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\hypersetup{
  pdftitle={NEIU G\&ES MA Thesis},%
  pdfauthor={Neil Best <nbest@alum.mit.edu>},%
  pdfsubject={land use / land cover},%
  pdfkeywords={agriculture}{United States},%
  pdffitwindow=true,%
  pdfstartview={FitH}
}
\usepackage[all]{hypcap}
\usepackage{multirow}

\begin{document} 
\bibliographystyle{chicago}

\title{Synthesis of a complete land use\slash land cover data set for the
  conterminous United States emphasizing accuracy in area and
  distribution of agricultural activity}
 

\othermasters{Master of Arts}{M.A.}  
\department{Geography \& Environmental Studies}

\author{Neil A. Best}
\degreeyear{August~2011}



\maketitle

%\includepdf[pages={2,1}]{neiuForms.pdf}
%!pdfTeX error: pdflatex (file ./neiuForms.pdf): PDF inclusion: invalid font in reference type <dictionary>

\frontmatter

\begin{abstract} This paper presents an effort to produce a new land
  cover data set for the conterminous United States of America (cUSA)
  that augments available agricultural land use data with other uses
  and natural covers to create a complete landscape characterization.
  Using the Agland2000 data set as a benchmark we formulate a
  hybridization of the MODIS Land Cover Type (MLCT) for 2001 and the
  2001 National Land Cover Database (NLCD) that is particularly
  tailored to serve as an initialization data set for long-term
  economic land use change models.  In order to strike a balance
  between spatial precision and local diversity of use and cover the
  new data set has lower resolution than the MLCT ($5'$ vs. $15''$)
  but represents land use/land cover (LULC) components as sub-pixel
  fractions rather than discrete categories.  After aggregating to the
  $5'$ grid we present a method for decomposing the natural
  vegetation/cropland mosaic class found in MLCT into constituent
  classes as a function of the local landscape.  We then quantify its
  contribution to aggregate acreages by class, particularly cropland.
  We compensate for the absence of certain fine-grained details from
  MLCT, such as rural transportation networks, small settlements,
  linear water features, and wetlands, mainly due to sensor
  resolution, by incorporating corresponding components of the NLCD,
  after similar reclassification and aggregation, as a set of offsets
  to the MLCT-derived fractions.  The 175Crops2000 data set, valuable
  for its basis in per-crop agricultural production statistics, is
  used as a guide to further decompose the cropland areas into a set
  of crop-specific sub-categories designed to facilitate the economic
  modeling goals of the simulations that will be initialized by this
  data product.  The final classification scheme is conceptually
  equivalent to a stack of spectral bands with the additional property
  that the components of each pixel sum to unity.  Its classification
  scheme is a mixture of a simplified version of the IGBP schema used
  in MLCT and a disaggregation of the monolithic cropland class that
  differentiates among the world's major commodity crops.  At each
  step of refinement we show that overall spatial distribution of
  cropland across the study area improves relative to the Aglands2000
  data set.  We close with a discussion of how this method might be
  applied globally and to successive years in the MLCT time series.
\end{abstract}


\chapter*{Acknowledgments}

\noindent This thesis is dedicated to my son, Leo.  Son, I began
working on this degree before you were born and my commitment to
completing it was sustained by my desire to demonstrate to you that in
life we finish what we have started.

\vspace{12pt}
\noindent I could not have completed this paper over the past year
and, by extension, my degree over more years than I care to mention
without the support of my loving wife, Laura.

\vspace{12pt}
\noindent I want to thank Dr. Nicholas Kouchoukos of Lanworth,
Inc. for throwing me in the deep end of applying the open-source
geospatial software tool chain to spatial analysis of agriculture.

\vspace{12pt}
\noindent This work was made possible through the support of my
employer, the Computation Institute at the University of Chicago, and
its director, Dr. Ian Foster under the Community Integrated Model of
Economic and Resource Trajectories for Humankind project (CIM-EARTH,
\url{http://www.cim-earth.org/}).

\vspace{12pt}
\noindent My thesis committee was comprised of Dr. Monika Mihir
(chair), Dr. Erick Howenstine (department head), both of the
Department of Geography \& Environmental Studies at Northeastern
Illinois University, and Dr. Joshua Elliott from the Computation
Institute.  I deeply appreciate their guidance and support through all
stages of this project.


\tableofcontents 
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column %% is 1 inch wide and left-justified
\chapter{List of Abbreviations}

\begin{symbollist*}
\item[175Crops2000] Harvested Area and Yields of 175 crops (M3-Crops
  Data) \citep{Monfreda2008}
\item[Agland2000] Agricultural Lands in the Year 2000 (M3-Cropland and
  M3-Pasture Data) \citep{Ramankutty2008}
\item[AVHRR] Advanced Very High Resolution Radiometer
\item[CIM-EARTH] Community Integrated Model of Economic and Resource
  Trajectories for Humankind
\item[cUSA] conterminous (contiguous) Unites States of America, the ``lower 48''
\item[GADM] Global Administrative Areas, \url{http://www.gadm.org/}
\item[GIAM] Global Irrigated Areas Map
\item[GIS] Geographic Information Systems
\item[GMRCA] Global Map of Rainfed Crop Areas
\item[GLC2000] Global Land Cover 2000 \citep{EC2003}
\item[GRASS] Geographic Resources Analysis Support System, \url{http://grass.osgeo.org/}
\item[IGBP] International Geosphere-Biosphere Programme
\item[LULC] land use / land cover
\item[MODIS] Moderate Resolution Imaging Spectroradiometer
\item[MLCT] MODIS Land Cover Type \citep{MLCT}
\item[NLCD] National Land-Cover Database, 2001 \citep{Homer2004}
\item[PEEL] Partial Equilibrium Economic Land use model
\item[PLSS] Public Land Survey System
\item[RMSE] root of the mean squared error
\item[SPAM] Spatial Production Allocation Model
\item[SPOT] Syst\`eme pour l'Observation de la Terre

\end{symbollist*}

%% Create a List of Symbols. The left column 
%% is 0.7 inch wide and centered
\chapter{List of Symbols}

\begin{symbollist}[0.7in]
\item[$A_{min}$] Minimum sub-pixel fraction possible for primary cover
  given in MLCT base data
\item[$A_s$] Sub-pixel fraction of secondary cover type, function of
  classification confidence level and $A_{min}$
\item[$A_p$] Sub-pixel fraction of primary cover type, function of
  classification confidence level and $A_{min}$
\item[$\hat\theta$] Predicted sub-pixel fraction
\item[$\theta$] Observed sub-pixel fraction
\item[$'$] minute of arc, 1/60th of a degree
\item[$''$] second of arc, 1/60th of a minute, 1/3600th of a degree
\item[{[0,1]}] interval from 0 to 1, inclusive of 0 and 1; $0 \leq x \leq 1$ 
\item[[0,1)] interval from 0 to 1, inclusive of 0 but but not 1, $0 \leq x < 1$ 
%\item[$ \left[ 0,1 \right] $] interval from 0 to 1, inclusive of 0 and 1; $0 \leq x \leq 1$ 
%\item[$ \left[ 0,1 \right) $] interval from 0 to 1, inclusive of 0 but but not 1, $0 \leq x < 1$ 
\end{symbollist}

\todo{fix interval/set-builder notation in symbol list}

\mainmatter

\todototoc
\listoftodos

\include{introduction}
\include{datasets}
\include{analysis}

\chapter{Conclusions}
\label{cha:conclusions}

The goal of this study was to produce a LULC data set that was as
accurate as possible with respect to its representation of the
distribution of agricultural production and that also offers a
reasonable characterization of non-crop covers and land use beyond
those agricultural uses.  We have accomplished that.  In doing so we
have adopted a sub-pixel data structure for conveying land use and
land cover information, albeit at a low spatial resolution by today's
remote sensing and GIS standards.  However, we hope that our readers
will consider that this data structure has particular mathematical
properties that may make it useful for their applications.  The
ability to perform raster algebra on these stacks of maps made it
possible to apply scaling factors and offsets with concise syntax in
the \texttt{R} language that would not have been feasible in a
discrete, categorical framework.

We maintain that the reproducible research aspect of this study was
critical to its success.  By elaborating the analysis in an
interactive environment where every component of every data structure
is subject to inspection many missteps were discovered in the course
of our work.  In other GIS analysis environments it might have been
too difficult to perform basic sanity checks on intermediate outputs
before moving on and too easy to rely on a sense of ``everything looks
right'' in a GUI environment.  The ability to point to a body of
source code that expresses the steps of the analysis is a poignant
example of reproducibility, a pillar of the scientific method that has
fallen out of vogue because of the complexity of modern spatial
analysis until the recent emergence of applicable software tools
coupled with adequate computing resources.

This analysis would not have been possible without the \texttt{raster}
package for \texttt{R} developed by Hijmans, van~Etten and other
contributors.  We consider this interface to geospatial raster data
sets in the \texttt{R} statistical analysis environment an important
contribution to spatial analysis and a laudable accomplishment because
it unleashes the power of a sophisticated, popular, open-source, free
software programming language for statistical operations on large
geospatial raster data sets.  We expect that this demonstration will
foster additional interest in and use of this software, as well as
contribution to its continuing development.  Directions for possible
enhancement that would increase the utility of this package based on
our experience include streamlining a truly functional programming
interface by improving on the existing \texttt{overlay()} function,
harnessing available \texttt{R} extensions for parallelism and porting
core functionality to a \texttt{C} or \texttt{C++} library to improve
performance, and improving the visualization interface, perhaps
through application of the \texttt{ggplot2} package as we have done
here.

In the CIM-EARTH/PEEL research agenda the next logical extension of
the envisioned land use transition model would be to apply it to a
global study area.  Once a method for creating a global initialization
data set for the year 2001 is formulated we would like to apply that
method to the subsequent years of the MLCT time series.  In order to
do so we would need ancillary data that spatially extends the aspects of the
NLCD that we have employed and temporally extends the information
given in the Ramankutty \& Monfreda data sets.  At this time a method
for calculating the correction offsets for over-estimation of cropland
and under-estimation of inland water features, wetlands, and
development/transportation infrastructure over a wider area with
greater time depth has not been identified.  Only with this
information in hand were we able bring MLCT cropland and Agland2000
cropland into close enough agreement to minimize the mathematical
manipulation necessary to reasonably quantify the non-crop cover and
use classes with the desired fidelity to the best-available rasterized
agricultural census data.

In the absence of high-resolution data on rural development, being the
low-density portion of PEEL's ``urban'' class that falls below MLCT's
detection threshold we propose that it might be possible to model the
over-estimation factor of the MLCT cropland class.  This factor would
be defined as the ratio of total area encompassed by the MLCT cropland
classification to acreage actually under cultivation and could
potentially be modeled as a function of classification confidence and
secondary class using the data described and produced here as a
training set.  The null hypothesis in the formulation of such a model
is that there is enough diversity among agricultural landscapes in our
cUSA study area to adequately characterize agricultural landscapes
around the world in this regard.  Similarly it might be possible to
directly model the ``urban'' percentage below the MLCT detection
threshold as a function of population density and agricultural
productivity, identifying said threshold in the process.  There is a
clear dependency between these offsets in agriculturally productive
regions so modeling them in conjunction somehow may be
constructive.  We expect that global offsets for the water and
wetland classes will be harder to obtain without corresponding proxy
statistics with which to formulate a model but perhaps we can expect
greater availability of spatially explicit catalogs of ecological
services and sensitive/protected areas in the near future that would
close these gaps in the available information.

\todo{Should we elaborate on this validation exercise in the conclusion or just leave it out?}

Comparison of this data to other available LULC characterizations,
particularly the Major Land Use (MLU) data and the Cropland Data Layer
(CDL) from the USDA, would provide useful validation metrics.


\backmatter

\bibliography{thesis}

\appendix

\todo{Clean up source code by removing commented code that is no
  longer useful}
\todo{Fix problems with appendix headings}


\chapter{Source Code: Data Sets}

\section*{R helper functions}
\lstinputlisting{code/peel.R}

\section*{R code embedded in the chapter}
\lstinputlisting{datasets.R}

\chapter{Source Code: Analysis}

\section*{R helper functions}
\lstinputlisting{code/analysis.R}

\section*{R code embedded in the chapter}
\lstinputlisting{analysis.R}

\end{document}